### 2021-08-02 paper.tex
added small table of content and new chapter (conclution and future work)
corrected background, changed the methodology diagram

	\tableofcontents

@@

	The project examines list of risk factors that are being traced out in brain
	tumor surveillance systems. Also the method proposed assures to be highly
	efficient and precise for brain tumor detection, classification and
	segmentation. To achieve this precise automatic or semi-automatic methods
	are needed. The project proposes an automatic segmentation method that
	relies upon \textit{ CNN (Convolution Neural Networks) }, \textit{ VGG 16 }
	and \textit{ Resent 50 }, determining small 7 x 7 kernels. By incorporating
	this single technique, segmentation and classification is accomplished. CNN
	(a ML technique) from NN (Neural Networks)wherein it has layer based for
	results classification.

@@

	\begin{figure}[h]
		\centering
		\includegraphics[width=1\linewidth]{imgs/methodology}
		\caption{Proposed Methodology}%
		\label{Proposed Methodology}
	\end{figure}

@@

	\chapter{Result}
	\label{chap:Res}

@@

>>>>

	{\small\tableofcontents}
	%\tableofcontents

@@

	The project examines list of risk factors that are being traced out in brain
	tumor surveillance systems. Also the method proposed assures to be highly
	efficient and precise for brain tumor detection, classification and
	segmentation. To achieve this precise automatic or semi-automatic methods
	are needed. The project proposes an automatic segmentation method that
	relies upon \textit{ CNN (Convolution Neural Networks) }, \textit{ VGG 16 }
	and \textit{ Resnet 50 }, determining small 7 x 7 kernels. By incorporating
	this single technique, segmentation and classification is accomplished. CNN
	(a ML technique) from NN (Neural Networks)wherein it has layer based for
	results classification.

@@

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.5\linewidth]{imgs/methodology}
		\caption{Proposed Methodology}%
		\label{Proposed Methodology}
	\end{figure}

@@

	\chapter{Experimental Result}
	\label{chap:Res}

@@

	\chapter{Conclusion and Future Work}
